Untitled

### 2020-11-11 MSOAmodel.Rmd

ComplexModels2 %>%
  group_by(Dependent) %>%
  summarise('Beats NULL' = sum(Accuracy>AccuracyNull)/n(), #How many times did the models beat NULL
            Accuracy = mean(Accuracy), #What was the mean accuracy
            'NULL Model' = mean(AccuracyNull),
           'Null Difference' = mean(Accuracy-AccuracyNull) #Mean difference relative to NULL
            )

@@

```{r}
KitchenSink2 <- as.formula(Reference ~RelativeAfford + RelativeTourismDens +
                            LADTourismDensity + AffordRatioScale + AffordRatioScale2 + LADMeanMedianRatio, Ego2TourismDens2+Ego2TourismDens)

@@

ComplexModels2 %>%
  group_by(Dependent) %>%
  summarise('Beats NULL' = sum(Accuracy>AccuracyNull)/n(), #How many times did the models beat NULL
            Accuracy = mean(Accuracy), #What was the mean accuracy
            'NULL Model' = mean(AccuracyNull),
           'Null Difference' = mean(Accuracy-AccuracyNull) #Mean difference relative to NULL
            )
```

>>>>

ComplexModels2 %>%
  group_by(Dependent) %>%
  summarise('Beats NULL' = sum(Accuracy>AccuracyNull)/n(), #How many times did the models beat NULL
            Accuracy = mean(Accuracy), #What was the mean accuracy
            'NULL Model' = mean(AccuracyNull),
           'Null Difference' = mean(Accuracy-AccuracyNull),
                                    Sens = mean(Sensitivity),
           spec = mean(Specificity)#Mean difference relative to NULL
            )

@@

```{r}
KitchenSink2 <- as.formula(Reference ~RelativeAfford + RelativeTourismDens +
                            LADTourismDensity + AffordRatioScale + AffordRatioScale2 + LADMeanMedianRatio, Ego2TourismDens2+Ego2TourismDens + AffordRatioScale2*TourismDensity)

Formulatest <-  as.formula(Reference ~ TourismDensity+ AffordRatio + AffordRatioScale2)

set.seed(1983)
TestResample <- vfold_cv(LADMean, v = 5, repeats = 20, strata = "HighFinance")

@@

ComplexModels2 <- c("HighFinance", "HighLUP", "LADHighVal") %>%
  map_df(~{
    print(.x)
    ResOut2 <- MSOAMean2 %>%
      rename_(Reference = .x) %>%
      ResampledModelPerf(., TestResample, Formulatest, LADData = LADMean) %>%
      mutate(Dependent = .x)
})

ComplexModels2 %>%
  group_by(Dependent)%>%
  summarise('Beats NULL' = sum(Accuracy>AccuracyNull)/n(), #How many times did the models beat NULL
            Accuracy = mean(Accuracy), #What was the mean accuracy
            'NULL Model' = mean(AccuracyNull),
           'Null Difference' = mean(Accuracy-AccuracyNull),
                                    Sens = mean(Sensitivity),
           spec = mean(Specificity)#Mean difference relative to NULL
            )

AnalyzePreds <- c("HighFinance", "HighLUP", "LADHighVal") %>%
  map_df(~{
    print(.x)
    ResOut2 <- MSOAMean2 %>%
      rename_(Reference = .x) %>%
      ResampledModelPerfPreds(., TestResample, Formulatest, LADData = LADMean) %>%
      mutate(Dependent = .x,
             row = 1:n())
})

test <- AnalyzePreds %>%
  mutate(Predictions = Predictions>0.5) %>%
  select(Predictions, Dependent, sample, row) %>%
  spread(key = Dependent, value = Predictions)

test2 <- AnalyzePreds %>%
  mutate(Predictions = Predictions>0.5) %>%
  select(Reference, Dependent, sample, row) %>%
  spread(key = Dependent, value = Reference)

confusionMatrix(data = test$HighLUP & test$LADHighVal, test2$HighFinance)

confusionMatrix(test$HighFinance, test2$HighFinance)

confusionMatrix(test$HighLUP, test2$HighLUP)

confusionMatrix(test$LADHighVal, test2$LADHighVal)

### 2020-11-11 PaperCode.Rmd

schedule 2 part 5 section

Palgrave nature inter-discplinary journel
https://www.nature.com/palcomms/for-authors#edboard

poss editors
Dr Lei Wang, manchester Urban
Tim Hall, university winchester

maybe
Trifon I Missov, Max planck demographics

reviewr
Glen Bramley at herriot watt

ian caswell ucl mega journel
Kathrine sharp

Reviewers on plos

search term: data mining
César A Hidalgo
Massachusetts Institute of tech

search term: demography
Celine Rozenblat
University of Lausanne
SWITZERLAND

Heidi Harriman Ewen
University of Georgia
UNITED STATES

The information provided in response to your request is copyright Gateshead Council unless otherwise endorsed. Granting access to this information under the Freedom of Information Act does not permit you to re-use the information provided for commercial purposes, for photocopying or reproduction in any form. If you wish to re-use the information you need to apply for a Licence. You can do this by writing to Tanya Rossington, Information Rights Officer, Corporate Services and Governance, 1st Floor, Civic Centre, Regent Street, Gateshead, NE8 1HH. You may be required to pay a fee or comply with conditions for permitted re-use.

@@

##Non-Dataset LADs
This bootstrapping is done to get the data needed to predict across the whole of Wngland and Wales
```{r}
#Filter out all the LADs for the data we have, ake dataframe that can be sampled
AllOtherLADsdf <- EW2 %>%
  filter(!(LAD11CD %in% DATAdf$LAD11CD)) %>%
  select(LSOA11CD:Pop, MSOA11CD, LAD11CD, LAD11NM)%>%
  mutate(LowUse = 0) 
#Bootstrap
setwd(file.path(basewd, "BootstrapAllLADs"))
BootstrapAllData(AllOtherLADsdf, LimitValue = 1.4e5, Reps = 501, GroupingVars = "MSOA11CD")

@@

}
```

@@

@@

```{r}
setwd(DataFolder)
WelshTax <- read_csv("WelshCTax.csv", skip = 6, n_max = 23) %>%
  select(-X1) %>%
  mutate(CouncilTax = rowSums(.[-1])*1000) %>%
  rename(LAD11NM = X2) %>%
  left_join(., MSOAtoLAD %>% 
              select(LAD11CD, LAD11NM) %>%
              distinct(LAD11NM, .keep_all = T)) %>%
  filter(!is.na(LAD11CD)) %>%
    select(LAD11CD, CouncilTax)

@@

@@

>>>>

@@

##Non-Dataset LADs
This bootstrapping is done to get the data needed to predict across the whole of England and Wales
```{r}
#Filter out all the LADs for the data we have, ake dataframe that can be sampled
AllOtherLADsdf <- EW2 %>%
  filter(!(LAD11CD %in% DATAdf$LAD11CD)) %>%
  select(LSOA11CD:Pop, MSOA11CD, LAD11CD, LAD11NM)%>%
  mutate(LowUse = 0) 
#Bootstrap
setwd(file.path(basewd, "BootstrapAllLADs"))
BootstrapAllData(AllOtherLADsdf, LimitValue = 1.4e5, Reps = 501, GroupingVars = "MSOA11CD")

@@

@@

#2nd homes and Tourism
```{r}

TourismLAD <- Tourism %>%
  group_by(LAD11CD) %>%
  summarise_if(is.numeric, sum, na.rm = T) %>%
  bind_cols(Tourism %>% group_by(LAD11CD) %>% summarise(LAD11NM =first(LAD11NM)),.) %>%
  ungroup

ScndhomesCensus <- read_xlsx(path = file.path(DataFolder, "Census2011secondHomes.xlsx"), sheet = 3, skip = 13)[,1:7] %>%
  mutate(LAD11NM = ifelse(is.na(X__1), X__2, X__1)) %>%
  select(LAD11CD = K04000001, LAD11NM, ScndHomes = X__5) %>% # Pop = X__4,
  filter(!is.na(ScndHomes)) %>%
  #Replace changed codes
  mutate(LAD11CD = case_when(LAD11NM == "St Albans"~"E07000240",
                             LAD11NM =="Welwyn Hatfield"~"E07000241",
                             LAD11NM =="Northumberland UA 6"~"E06000057",
                             LAD11NM =="East Hertfordshire"~"E07000242",
                             LAD11NM =="Stevenage"~"E07000243",
                             LAD11NM =="Gateshead"~"E08000037",
                             TRUE~ LAD11CD)) %>%
  select(-LAD11NM) %>%
  left_join(TourismLAD, ., by = "LAD11CD") %>%
  mutate(TourismDens = (Guest + Hotel)/Homes,
         ScndHomesDens = ScndHomes/Homes) %>%
  filter(!is.na(LAD11CD)) %>%
  mutate(Perc2ndHomes = ScndHomes/sum(ScndHomes))

#not a lot of corellation
cor(ScndhomesCensus$TourismDens, ScndhomesCensus$ScndHomesDens)

#no real pattern
ScndhomesCensus %>%
  filter(TourismDens<0.1) %>%
ggplot(aes(x = TourismDens, ScndHomesDens)) + geom_point()

test <- left_join(LADMean, ScndhomesCensus, by = "LAD11CD")

sum(test$Perc2ndHomes)

rm(TourismLAD);
```

@@

```{r}
setwd(DataFolder)

WelshTax <- read_csv("WelshCTax.csv")

WelshTax <- read_csv("WelshCTax.csv", skip = 4, n_max = 23) %>%
  select(-X1) %>%
  mutate(CouncilTax = rowSums(.[-1])*1000) %>%
  rename(LAD11NM = X2) %>%
  left_join(., MSOAtoLAD %>% 
              select(LAD11CD, LAD11NM) %>%
              distinct(LAD11NM, .keep_all = T)) %>%
  filter(!is.na(LAD11CD)) %>%
    select(LAD11CD, CouncilTax)

@@

#For press office

test <- EmptyTax %>%
  select(LAD11CD, LAD11NM, Homes, LowUse, HomesMedian, LowUseMedian, LowUsePerc, MedianDiff, MedianDiffRatio, EmptyTax, EmptyOfCouncil, TaxPop)
write_csv(test, file.path(basewd, "Key Figures by Council.csv"))

@@

#Key figures
```{r}

#The top 3 LSOA for each LAD in terms of perc low use
TopLSOA <- DATAdf %>% 
  ungroup %>%
  arrange(-LowUsePerc) %>%
  group_by(LAD11CD) %>%
  slice(1:3)
  #top_n(., 3, LowUsePerc)

#The value of the low use property
TotalValueProperty <- DATAdf %>%
  group_by(LAD11CD) %>%
  summarise(LAD11NM = first(LAD11NM),
            LUPSValue = sum(LowUse*MeanPrice, na.rm = T),
            HomesValue = sum(Homes*MeanPrice, na.rm = T)) %>%
  mutate(LUPofTotMarket = LUPSValue/HomesValue)

Key_Areas <- read.csv(file.path("/home/jonno/Downloads", "LAs for Jonathan.csv")) %>% select(LAD11CD, news_area)

TopLSOA <- Key_Areas %>%
  left_join(TopLSOA, .) %>%
  filter(!is.na(news_area))

TotalValueProperty <- Key_Areas %>%
  left_join(.,TotalValueProperty)

test <-LADMean %>%
 #filter(LAD11NM == "Barnet")
  filter(Region == "E12000007") %>%
  select(LAD11NM, LowUse, LowUseMean, HomesMean, AffordRatio, MedianDiff, MedianDiffRatio) %>%
  mutate_if(is.numeric, signif, digits = 3)

write.csv(test, file.path("/home/jonno", "LondonMSOA.csv"))

test <- DATAdf %>%
filter(LAD11CD == "E06000052") %>%
  write.csv(file.path("/home/jonno/Downloads", "Brighton.csv"))

write.csv(TopLSOA, file.path("/home/jonno/Downloads", "TopLSOA.csv"))
write.csv(TotalValueProperty, file.path("/home/jonno/Downloads", "TotalValueProperty.csv"))

LSOAshape <- st_read(LSOAshapedata) %>%
  left_join(DATAdf, by = c("lsoa11cd"="LSOA11CD")) %>% filter(grepl("Bradford",LAD11NM)) #filter(grepl("E09000003",LAD11CD))

LSOAshape %>%
ggplot(.)+  geom_sf(aes(fill = LowUsePerc))  +
   theme(axis.title.x=element_blank(),
          axis.text.x=element_blank(),
          axis.ticks.x=element_blank(),
          axis.title.y=element_blank(),
          axis.text.y=element_blank(),
          axis.ticks.y=element_blank())+
  ggtitle("Low use Percentage by lsoa in Trafford")+
  scale_fill_viridis_c()

test <- TotalValueProperty  %>%
  filter(grepl("(Allerdale)|(Copeland)|(Carlisle)|(South Lake)|(Barrow)|(Eden)", LAD11NM))

test <- MSOAMean %>%
filter(LAD11CD == "E06000052")

```{r}
CorePstCd %>%
 filter(Region == "E12000007") %>%
  distinct(LAD11CD, .keep_all = T) %>%
  select(LAD11CD, LAD11NM) %>%
  filter(!(LAD11CD %in% (LADMean %>%  filter(Region == "E12000007") %>% pull(LAD11CD))))

### 2020-11-11 testCode.Rmd

CorePstCd <- PstCdLSOA.raw %>%
  left_join(EW2, by = c("lsoa11cd" = "ECODE")) %>%
  select(Postcode, lsoa11cd, LAD11CD, LAD11NM,Admin_ward_code = Admin_ward_code.x, WD16NM)

@@

@@

LSOABiz <- CompanyData %>%
  filter(!is.na(LAD11CD)) %>%
  mutate(X6 = gsub("( AND PREMISES)|( & PREMISES)", "",X6),
         X6 = gsub("(AND PREMISES)|(& PREMISES)", "",X6)) %>%
  group_by(lsoa11cd, X6) %>%
  summarise(counts = n(),
            LAD11CD = first(LAD11CD),
            LAD11NM = first(LAD11NM),
            Admin_ward_code = first(Admin_ward_code),
            WD16NM = first(WD16NM))

@@

@@

Look at Westminster

@@

West <- LSOABiz %>%
  filter(LAD11CD=="E09000033")

Catering <- West %>%
  filter(grepl("SELF CATER",X6))

@@

table(is.na(test$lsoa11cd))

test2 <- test %>%
  filter(!is.na(lsoa11cd)) %>%
  group_by(lsoa11cd) %>%
  summarise(counts = n(),
            LAD11CD = first(LAD11CD),
            LAD11NM = first(LAD11NM),
            Admin_ward_code = first(Admin_ward_code),
            WD16NM = first(WD16NM)) %>%
  arrange(desc(counts))

examin <- test %>% 
  filter(lsoa11cd =="E01006854")

@@

Flats3<- Flats %>% left_join(PstCdLSOA.raw)%>%
   group_by(lsoa11cd) %>%
  summarise(Total = n()) %>%
#  left_join(EW2, by = c("lsoa11cd" = "ECODE")) %>%
  rename(LSOA_CODE = lsoa11cd)

>>>>

CorePstCd <- PstCdLSOA.raw %>%
  left_join(EW2, by = c("lsoa11cd" = "ECODE")) %>%
  select(Postcode,LSOA11CD= lsoa11cd, LAD11CD, LAD11NM, MSOA11CD, Pop)

@@

#How many of the postcodes are matched?
sum(!is.na(CompanyData$LSOA11CD))/nrow(CompanyData) #this is a high number which is totally acceptable

@@

#Find each type of business
LSOABiz <- CompanyData %>%
  filter(!is.na(LAD11CD)) %>%
  mutate(X6 = gsub("( AND PREMISES)|( & PREMISES)", "",X6),
         X6 = gsub("(AND PREMISES)|(& PREMISES)", "",X6)) %>%
  group_by(LSOA11CD, X6) %>%
  summarise(counts = n(),
            LAD11CD = first(LAD11CD),
            LAD11NM = first(LAD11NM),
            MSOA11CD = first(MSOA11CD))

@@

Hotel <- FirmCounts %>%
  filter(grepl("(HOTEL)|(HOSTEL)",X6))

Guest <- FirmCounts %>%
  filter(grepl("(GUEST)",X6))

sum(Guest$counts)

@@

#Tourism to Lups

I want to be able to plot the tourism density to deprivation and overlay the catagories and see what happens

@@

setwd("/home/jonno/Dropbox/SSE/Empty Homes/BootstrapMSOA")

 LADAfford2 <- list.files(getwd()) %>%
   map_df(~readRDS(.x)) %>%
   left_join(select(IncomeEst, Yearly.income, MSOA11CD), by = "MSOA11CD") %>%
   ungroup %>%
   mutate(MSOAAffordRatio = MSOAHomesMedian/Yearly.income,
          MSOAHighVal = MSOAHomesMedian< MSOALowUseMedian, #Reference Variable
          MOSAHighLUP = MSOALowUsePerc >median(MSOALowUsePerc))  #Reference Variable

 %>%
   group_by(LAD11CD, ID) %>%
   summarise(LADHomesMedian = first(LADHomesMedian),
             MedianLowUse = first(LADLowUseMedian)) %>%
   group_by(LAD11CD) %>%
   summarise(LADHomesMedian = mean(LADHomesMedian, na.rm = T),
             MedianLowUse = mean(MedianLowUse, na.rm = T)) %>%
   left_join(MSOAtoLAD,., by = "LAD11CD") %>%
   filter(!is.na(LADHomesMedian)) %>% # keep only the LADs that I have data for
   left_join(., IncomeEst, by = "MSOA11CD") %>%
  group_by(LAD11CD) %>%
  summarise(Yearly.income = weighted.mean(Yearly.income, Homes),
            LADHomesMedian = weighted.mean(LADHomesMedian, Homes)) %>%
   mutate(AffordRatio = LADHomesMedian/Yearly.income,
          AffordRank = rank(AffordRatio),
          AffordRank = scale(AffordRank),
          AffordRank2 = AffordRank^2)

Tourism <- CompanyData %>%
  filter(!is.na(LAD11CD))%>%
  filter(grepl("(SELF CATER)|(HOLIDAY)|(HOTEL)|(HOSTEL)|(GUEST)",X6))  %>%
  mutate(Guest = grepl("(SELF CATER)|(HOLIDAY)|(GUEST)",X6),
         Hotel = grepl("(HOTEL)|(HOSTEL)",X6))
   group_by(LSOA11CD, X6) %>%
  summarise(counts = n(),
            LAD11CD = first(LAD11CD),
            LAD11NM = first(LAD11NM),
            MSOA11CD = first(MSOA11CD),
            Pop = first(Pop),
            Guest = sum(Guest),
            Hotel = sum(Hotel))

Tourism2 <- Tourism %>%
  group_by(LAD11CD, LAD11NM) %>%
  summarise(Tourism = sum(counts),
            Pop = sum(Pop))

# Only used if bootdeets two exists, which is created in the MSOAmodel rmd
testLAD <- Tourism2 %>% #
  left_join(BootDeets2,.) %>% 
  mutate(TourismDensity =Tourism/Homes,
         TourismDensityRank = percent_rank(TourismDensity)) %>%
  left_join(LADAfford2, by = "LAD11CD") %>%
  #mutate(Extent = AffordRatio) %>%
  left_join(select(LADDep, LAD11CD, Extent, Average.rank)) %>%
  mutate(ExtentRank = percent_rank(-Extent),
         ExtentRank2 = (Extent-0.5)^2,
         TourDepCat = case_when( 
           TourismDensityRank>=0.5 & ExtentRank>=0.5 ~ 1, #wealthly high tourism
           TourismDensityRank>=0.5 & ExtentRank<0.5 ~ 2, #Wealthy Low tourism
           TourismDensityRank<0.5 & ExtentRank>=0.5 ~3, #Poor High tourism
           TRUE ~ 4                                          #Poor low tourism
         ) %>% as.factor,
         Reference = Catagory==1|Catagory==2)

#This plot means we may be able to separate High low use from Low low use.
testLAD  %>%
  ggplot(aes(x= AffordRank2, y = TourismDensityRank, colour = Reference)) + geom_point()
+
  geom_hline(yintercept = 0.5) +
  geom_vline(xintercept = 0.5)

testLAD %>%
  filter(Catagory==1, TourDepCat==3) %>% select(Catagory, TourDepCat, LAD11NM)

 testLAD %>%
  filter(Catagory %in% c(3,4), TourDepCat==1) %>% select(Catagory, TourDepCat, LAD11NM)

#
#
#This model is the best for predicting LADs with high value LUPs-- Can include wales!
#
  #OpenFormula <- as.formula(Reference ~ AffordRank+ AffordRank2+ TourismDensityRank)

#local tourism.
number of hotels within 1 MSOA

MSOAEgoListDist1 <- ego(MSOAgraph, 1) %>%map(~names(.x))
names(MSOAEgoListDist1) <- get.vertex.attribute(MSOAgraph, "name")

 NeighbourhoodQuartiles <- names(MSOAEgoListDist1) %>% map_df(~{

   print(.x)
   target <- MSOAEgoListDist1[[.x]]
   test <- Tourism %>%
     filter(MSOA11CD %in% target) %>%
     ungroup %>%
     summarise(
               Hotel = sum(Hotel),
               Guest = sum(Guest))

 }) %>%
  mutate(MSOA11CD =  names(MSOAEgoList))

 test <- NeighbourhoodQuartiles %>%
   left_join(MSOAtoLAD)

#How do I make an MSOA version? of tourism density?
2654
```{r}
MSOAtest<- CompanyData %>%
  filter(!is.na(LAD11CD))%>%
  filter(grepl("(SELF CATER)|(HOLIDAY)|(HOTEL)|(HOSTEL)(GUEST)",X6))  %>%
   group_by(LSOA11CD) %>%
  summarise(counts = n(),
            Guest = sum(grepl("(SELF CATER)|(HOLIDAY)|(GUEST)",X6)),
            Hotel = sum(grepl("(HOTEL)|(HOSTEL)",X6)),
            LAD11CD = first(LAD11CD),
            LAD11NM = first(LAD11NM),
            MSOA11CD = first(MSOA11CD),
            Pop = first(Pop)) %>%
  group_by(MSOA11CD) %>%
  summarise(Tourism = sum(counts, na.rm = T),
            Hotel= sum(Hotel, na.rm = T),
            Guest = sum(Guest, na.rm = T),
            Pop = sum(Pop),
            LAD11CD = first(LAD11CD),
            LAD11NM = first(LAD11NM)) %>% #
  left_join(BootDeetsMean,., by = "MSOA11CD") %>%
  mutate(Tourism = ifelse(is.na(Tourism), 0, Tourism),
         Guest = ifelse(is.na(Guest), 0, Guest),
         Hotel = ifelse(is.na(Hotel), 0, Hotel),
         TourismDensity =scale(Tourism/Homes),
         HotelDensity =scale(Hotel/Homes),
         GuestDensity =scale(Guest/Homes),
         TourismDensityRank = percent_rank(TourismDensity),
         TourismDensityRankV2 = rank(TourismDensity, ties.method = "max"),
         HotelDensityRank = percent_rank(HotelDensity),
         GuestDensityRank = percent_rank(GuestDensity),
         AffordRatio = scale(AffordRatio),
         AffordRatio2 = AffordRatio^2)  %>% 
  left_join(NeighbourhoodQuartiles %>% rename(Ego1Hotel= Hotel, Ego1Guest = Guest), by = "MSOA11CD") %>%
  mutate(Ego1Guest = ifelse(is.na(Ego1Guest), 0, Ego1Guest),
         Ego1Hotel = ifelse(is.na(Ego1Hotel), 0, Ego1Hotel))

ModelMSOAdf <- MSOAtest %>%
  mutate(ExtentRank = percent_rank(AffordRatio),
         TourDepCat = case_when( 
           TourismDensityRank>=0.5 & ExtentRank>=0.5 ~ 1, #wealthly high tourism
           TourismDensityRank>=0.5 & ExtentRank<0.5 ~ 2, #Wealthy Low tourism
           TourismDensityRank<0.5 & ExtentRank>=0.5 ~3, #Poor High tourism
           TRUE ~ 4                                          #Poor low tourism
         ) %>% as.factor)  %>%
   mutate(MedianPercDiff = (MSOALowUseMedian-MSOAHomesMedian)/MSOAHomesMedian,
         PercLowUse = LowUse/Homes,
         RankLowUse = percent_rank(PercLowUse),
         RankMedianDiff = percent_rank(MedianPercDiff),
         Catagory = case_when( 
           RankLowUse>=0.5 & RankMedianDiff>=0.5 ~ 1, #High low use and High price difference
           RankLowUse>=0.5 & RankMedianDiff<0.5 ~ 2, #High low Use and Low rank price difference
           RankLowUse<0.5 & RankMedianDiff>=0.5 ~3, # Low low use and high price difference
           TRUE ~ 4 #Low low use low price difference
         ) %>% as.factor,
        Reference = RankLowUse>0.5, #Catagory==1|Catagory==2,
         #Reference =MSOAHomesMedian<MSOALowUseMedian,
         spare = 1)

ModelMSOAdf   %>%
  ggplot(aes(x= AffordRank, y = TourismDensityRankV2, colour = Reference)) + geom_point() 
+
  geom_hline(yintercept = 0.5) +
  geom_vline(xintercept = 0.5)

ModelMSOAdf   %>%
  filter(Tourism == 0) %>%
  ggplot(aes(x= ExtentRank, y = LowUsePerc, colour = Catagory)) + geom_point()
+
  geom_hline(yintercept = 0.5) +
  geom_vline(xintercept = 0.5)

ModelMSOAdf  %>%
  ggplot(aes(x= RankLowUse, y = RankMedianDiff, colour = Guest>0)) + geom_point()

table(ModelMSOAdf$Guest>0, ModelMSOAdf$RankLowUse>0.5)

confusionMatrix(ModelMSOAdf$Tourism>0, ModelMSOAdf$RankLowUse>0.5)

#Model If a lot of LUPs

Modeldf <- ModelMSOAdf #testLAD

OpenFormula <- as.formula(Reference ~ Guest + Hotel + AffordRatio+ AffordRatio2)

set.seed(1983)
TestResample <- 1:100 %>% map(~  resample_partition(Modeldf , c(test = 0.2, train = 0.8)))

#Make a lot of models

ResOut <- 1:length(TestResample) %>% map_df(~{
  Mod2 <- Modeldf  %>%
  mutate(Reference = as.factor(Reference)) %>%
  slice(as.integer(TestResample[[.x]]$train)) %>%
  glm(formula = OpenFormula, data = ., family=binomial(link='logit'))

preds2<- Modeldf  %>%
  mutate(Reference = as.factor(Reference)) %>%
  slice(as.integer(TestResample[[.x]]$test)) %>%
predict(Mod2, ., type = "response")

ConfOut<-Modeldf  %>%
  mutate(Reference = as.factor(Reference)) %>%
  slice(as.integer(TestResample[[.x]]$test)) %>%
  pull(Reference) %>%
confusionMatrix(.,preds2>0.5)

ConfOut$overall %>% t %>% data.frame() %>% as.tibble

})

test <- tibble(truth = ConfOut, estimate = as.factor(preds2>0.5))
conf_mat(test, truth, estimate) %>%summary(wide= T)

MODOut <- 1:length(TestResample) %>% map_df(~{
  Mod2 <- Modeldf  %>%
  mutate(Reference = as.factor(Reference)) %>%
  slice(as.integer(TestResample[[.x]]$train)) %>%
  glm(formula = OpenFormula, data = ., family=binomial(link='logit'))%>%
    tidy

})

ggplot(MODOut, aes(x = term, y = estimate)) + geom_boxplot()

#
#        TREEEEEEEEEEEEEEEEEE
# 
OpenFormula <- as.formula(Reference ~ TourismDensityRank + AffordRatio+ AffordRatio2)

library(ranger)
ResOut <- 1:length(TestResample) %>% map_df(~{
  print(.x)
  Mod2 <- Modeldf  %>%
  mutate(Reference = as.factor(Reference)) %>%
  slice(as.integer(TestResample[[.x]]$train)) %>%
  ranger(formula = OpenFormula, data = . )

preds2<- Modeldf  %>%
  mutate(Reference = as.factor(Reference)) %>%
  slice(as.integer(TestResample[[.x]]$test)) %>%
predict(Mod2, ., type = "response")
preds2 <- preds2$predictions

ConfOut<-Modeldf  %>%
  mutate(Reference = as.factor(Reference)) %>%
  slice(as.integer(TestResample[[.x]]$test)) %>%
  pull(Reference) %>%
confusionMatrix(.,preds2)

ConfOut$overall %>% t %>% data.frame() %>% as.tibble

})

sum(ResOut$Accuracy>ResOut$AccuracyNull)/nrow(ResOut)
mean(ResOut$Accuracy)

#The models are significantly greater than the null model when using a paired t-test.
t.test(ResOut$Accuracy,ResOut$AccuracyNull, alternative = "greater", paired = T)

ResOut %>%
  ggplot(aes(x = (Accuracy - AccuracyNull))) + geom_density()

#Look at Westminster

West <- LSOABiz %>5
  filter(LAD11CD=="E09000033")

Catering <- West %>%
  filter(grepl("(SELF CATER)|(HOLIDAY)|(HOTEL)|(HOSTEL)(GUEST)",X6))

sum(Catering$counts)

@@

table(is.na(test$LSOA11CD))

test2 <- test %>%
  filter(!is.na(LSOA11CD)) %>%
  group_by(LSOA11CD) %>%
  summarise(counts = n(),
            LAD11CD = first(LAD11CD),
            LAD11NM = first(LAD11NM),
            Admin_ward_code = first(Admin_ward_code),
            WD16NM = first(WD16NM)) %>%
  arrange(desc(counts))

examin <- test %>% 
  filter(LSOA11CD =="E01006854")

@@

Flats3<- Flats %>% left_join(PstCdLSOA.raw)%>%
   group_by(LSOA11CD) %>%
  summarise(Total = n()) %>%
#  left_join(EW2, by = c("LSOA11CD" = "ECODE")) %>%
  rename(LSOA_CODE = LSOA11CD)
